Neural Networks as Dual Gaussian Processes for Sequential Learning

### 2023-08-31 papers/iclr-2024/main.tex
added authors

\usepackage{hyperref}
\usepackage{url}

@@

% \title{Neural Networks as Sparse Gaussian Processes via Dual Parameters}
\title{Neural Networks as Sparse Gaussian Processes for Sequential Learning}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review.

\author{Antiquus S.~Hippocampus, Natalia Cerebro \& Amelie P. Amygdale \thanks{ Use footnote for providing further information
about author (webpage, alternative address)---\emph{not} for acknowledging
funding agencies.  Funding acknowledgements go at the end of the paper.} \\
Department of Computer Science\\
Cranberry-Lemon University\\
Pittsburgh, PA 15213, USA \\
\texttt{\{hippo,brain,jen\}@cs.cranberry-lemon.edu} \\
\And
Ji Q. Ren \& Yevgeny LeNet \\
Department of Computational Neuroscience \\
University of the Witwatersrand \\
Joburg, South Africa \\
\texttt{\{robot,net\}@wits.ac.za} \\
\AND
Coauthor \\
Affiliation \\
Address \\
\texttt{email}
}

@@

\begin{abstract}
Deep neural networks are known to lack uncertainty estimates, struggle to incorporate new data, and suffer from catastrophic forgetting. We present a method that mitigates these issues by converting neural networks from weight-space to a low-rank function-space representation, via the so-called dual parameters. In contrast to previous work, our sparse representation captures the joint distribution over the entire data set, rather than only over a subset. This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance. We demonstrate the proposed approach for quantifying uncertainty in supervised learning and maintaining an expressive functional representation for sequential learning.\looseness-1
\end{abstract}

@@

\bibliography{bibliography}%zotero-library
% % \bibliography{iclr2024_conference}
\bibliographystyle{iclr2024_conference}

\clearpage
\appendix

@@

@@

{\color{red}{
\subsection{Uncertainty quantification in RL}
A key challenge in RL is balancing the trade-off between exploration and exploitation \cite{sutton2018reinforcement}.
%That is, should an agent select actions that it knows will lead to high reward %(exploitation), or should it
%select new ones in hope to discover actions leading to higher reward (exploration).
One promising direction to balancing this trade-off is to model the uncertainty associated with a learned transition dynamics model and use it to guide exploration.
Prior work has taken an expectation over the dynamic model's posterior \cite{deisenroth2011pilco,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
sampled from it (akin to Thompson sampling but referred to as posterior sampling in RL) \cite{dearden1999model,osbandMoreEfficientReinforcement2013},
and used it to implement optimism in the face of uncertainty using upper confidence bounds \cite{curiEfficient2020,jaksch2010near}.
No single strategy has emerged as a go-to method and we highlight that these strategies are only as good as their uncertainty estimates.
Previous approaches have used GPs \cite{deisenroth2011pilco,kamtheDataEfficient2018},
ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
and variational inference \cite{galImproving2016,houthooftVIME2017}.
However, each method has its pros and cons.
In this paper, we present a method which combines some of the pros from NNs with the benefits of GPs.
}}
% \todo{could try to implement Pathwise conditioning in function-space}

>>>>

% \usepackage{hyperref}
% \usepackage[colorlinks=true,linkcolor=black,allcolors=black,urlcolor=black,citecolor=black]{hyperref}
\usepackage[colorlinks=true,linkcolor=blue,allcolors=blue,urlcolor=black,citecolor=blue]{hyperref}
\usepackage{url}

@@

% \title{Neural Networks as Sparse Gaussian Processes via Dual Parameters}
\title{Neural Networks as Dual Gaussian Processes for Sequential Learning}

% Authors must not appear in the submitted version. They should be hidden
% as long as the \iclrfinalcopy macro remains commented out below.
% Non-anonymous submissions will be rejected without review.
% \iclrfinalcopy

% TODO do equal contribution properly
\author{Aidan Scannell\thanks{Equal contribution.}, Riccardo Mereu*, Ella Tamir, Paul Chang, Joni Pajarinen, \& Arno Solin \\
% Department of Electrical Engineering and Automation\\
Aalto University\\
Espoo, Finland\\
% Helsinki \\
% \texttt{aidan.scannell@aalto.fi} \\
\texttt{\{aidan.scannell,riccardo.mereu\}@aalto.fi}
% \texttt{\{aidan.scannell,riccardo.mereu,paul.chang,ella.tamir,joni.pajarinen,arno.solin\}@aalto.fi}
}

% \author{Aidan Scannell\thanks{ Use footnote for providing further information about author (webpage, alternative address)---\emph{not} for acknowledging funding agencies.  Funding acknowledgements go at the end of the paper.} \\
% \author{Aidan Scannell\thanks{Equal contribution.} \\
% % Department of Electrical Engineering and Automation\\
% Aalto University\\
% % Helsinki \\
% % \texttt{aidan.scannell@aalto.fi} \\
% \And
% Riccardo Mereu\thanks{Equal contribution.}\\
% % Department of Computer Science\\
% Aalto University\\
% % Helsinki \\
% % \texttt{riccardo.mereu@aalto.fi} \\
% \And
% Ella Tamir\\
% % Department of Computer Science\\
% Aalto University\\
% % Helsinki \\
% % \texttt{ella.tamir@aalto.fi} \\
% \And
% Paul Chang\\
% % Department of Computer Science\\
% Aalto University\\
% % Helsinki \\
% % \texttt{paul.chang@aalto.fi} \\
% \And
% Joni Pajarinen\\
% % Department of Electrical Engineering and Automation\\
% Aalto University\\
% % Helsinki \\
% % \texttt{joni.pajarinen@aalto.fi} \\
% \And
% Arno Solin\\
% % Department of Computer Science\\
% Aalto University\\
% % Helsinki \\
% % \texttt{arno.solin@aalto.fi} \\
% % \And
% % Ji Q. Ren \& Yevgeny LeNet \\
% % Department of Computational Neuroscience \\
% % University of the Witwatersrand \\
% % Joburg, South Africa \\
% % \texttt{\{robot,net\}@wits.ac.za} \\
% % \AND
% % Coauthor \\
% % Affiliation \\
% % Address \\
% % \texttt{email}
% }

% \author{%
%   Aidan Scannell\textsuperscript{\star} \\
%   Aalto University \\
%   Finnish Center for Artificial Intelligence \\
%   \texttt{aidan.scannell@aalto.fi}
%   \And
%   Riccardo Mereu\textsuperscript{\star} \\
%   Aalto University\\
%   \texttt{riccardo.mereu@aalto.fi}
%   \And
%   Paul Chang \\
%   Aalto University\\
%   \texttt{paul.chang@aalto.fi}
%   \And
%   Ella Tamir \\
%   Aalto University\\
%   \texttt{ella.tamir@aalto.fi}
%   \And
%   Joni Pajarinen \\
%   Aalto University\\
%   \texttt{joni.pajarinen@aalto.fi}
%   \And
%   Arno Solin \\
%   Aalto University\\
%   \texttt{arno.solin@aalto.fi}
% }

@@

\begin{abstract}
  Deep neural networks are known to lack uncertainty estimates, struggle to incorporate new data, and suffer from catastrophic forgetting. We present a method that mitigates these issues by converting neural networks from weight-space to a low-rank function-space representation, via the so-called dual parameters. This offers a compact and principled way of capturing uncertainty and enables us to incorporate new data without retraining whilst retaining predictive performance. We demonstrate the proposed approach for quantifying uncertainty in supervised learning, maintaining an expressive functional representation for continual learning and guiding exploration in model-based reinforcement learning.\looseness-1
\end{abstract}

@@

\newpage
\bibliography{bibliography}%zotero-library
% % \bibliography{iclr2024_conference}
\bibliographystyle{iclr2024_conference}

\clearpage
\appendix
\section*{Appendix}

@@

\subsection{Related work}
A key challenge in RL is balancing the trade-off between exploration and exploitation \cite{sutton2018reinforcement}.
%That is, should an agent select actions that it knows will lead to high reward %(exploitation), or should it
%select new ones in hope to discover actions leading to higher reward (exploration).
One promising direction to balancing this trade-off is to model the uncertainty associated with a learned transition dynamics model and use it to guide exploration.
Prior work has taken an expectation over the dynamic model's posterior \cite{deisenroth2011pilco,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
sampled from it (akin to Thompson sampling but referred to as posterior sampling in RL) \cite{dearden1999model,sasso2023posterior,osbandMoreEfficientReinforcement2013},
and used it to implement optimism in the face of uncertainty using upper confidence bounds \cite{curiEfficient2020,jaksch2010near}.
No single strategy has emerged as a go-to method and we highlight that these strategies are only as good as their uncertainty estimates.
Previous approaches have used GPs \cite{deisenroth2011pilco,kamtheDataEfficient2018},
ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
and variational inference \cite{galImproving2016,houthooftVIME2017}.
However, each method has its pros and cons.
In this paper, we present a method which combines some of the pros from NNs with the benefits of GPs.
% \todo{could try to implement Pathwise conditioning in function-space}

@@
